Adopting agile software development in the large organizations: A systematic literature review

### 2014-05-27 journal/article.tex
T: Continuous integration

@@

\begin{table}
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.42\textwidth}
                     >{\raggedright\arraybackslash}p{0.50\textwidth} }
        Investment for transformation      &  Described in  \\
        \midrule
        Agile project management tools  &
                P10, P11, P14, P16, P17, P26, P33,
                P41, P43, P44, P45, P48, P50 \\
        Proprietary agile material or documentation   & 
                P1, P2, P8, P14, P16, P23, P26, P29, P32, P45  \\
        Refurbishing work areas and other spaces   &
                P6, P22, P35, P36, P38, P42, P46, P48 \\
        \bottomrule
    \end{tabular}
    \caption{Investments aiming to make agile methods perform better}
    \label{table:transformation_investments}
\end{table}

@@

@@

>>>>

* Principle of build often? Principle of nightly builds or CI? Is this from XP?
  Is this an agile principle?

@@

\begin{table}
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.42\textwidth}
                     >{\raggedright\arraybackslash}p{0.50\textwidth} }
        Investment for transformation      &  Described in  \\
        \midrule
        Agile project management tools  &
                P10, P11, P14, P16, P17, P26, P33,
                P41, P43, P44, P45, P48, P50 \\
        Continuous builds and testing  &
                P5, P11, P16, P17, P25, P27, P34, P39, P42, P50 \\
        Proprietary agile material or documentation   & 
                P1, P2, P8, P14, P16, P23, P26, P29, P32, P45  \\
        Refurbishing work areas and other spaces   &
                P6, P22, P35, P36, P38, P42, P46, P48 \\
        \bottomrule
    \end{tabular}
    \caption{Investments aiming to make agile methods perform better}
    \label{table:transformation_investments}
\end{table}

@@

% Investing in continuous builds

Continuous builds and testing was reported to play an important role in scaling
the agile model up to large scale [P17, P34]. Many organizations were
experiencing problems when a daily build system was not in place. The main
problem was that progress was slowed down because of lacks in the build and
automated testing systems [P5, P27, P39, P50].
Other reasons for implementing build automation was the need for having stable
nightly builds [P5], builds were often broken when integration was attempted
[P27], and there were problems with timeliness in test execution [P11]. One case
reported that the entire infrastructure needed to be revamped to attain benefits
from the accelerated work pace of Scrum teams [P50].

When a general problem of frequent broken builds existed it was easy to acuire a
buy in for creating an organization-wide standard for automating builds and
tests [P11]. On the other hand, many cases emphasized that building the
continuous integration environment required a significant investment [P17, P34,
P42]. In order to have the focus and resources for creating a proper integration
environment a dedicated team was Some organizations appointed a dedicated team
to ensure the focus and resources for creating a proper integration environment
were available [P5, P16, P17].

Having daily builds was considered a significant advantage in the agile
implementation [P5, P16]. Having the continuous integration environment in place
cases reported that development time was reduced [P39], the build times were
significantly improved [P5, P42], teams could know on a daily basis whether
their code could be integrated [P17]. It was also reported that the
communication and trust between testing and development was improved [P42].

@@

* For instance, implementing continuous integration and automated builds was not
  explicitly stated as a factor contributing to the success of the
  transformation, although it is unquestionable that such systems are critical
  for maintaining quality and enabling frequent releases.
